Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
log compression => logarithmic compression

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients \gl{vincent: windows and hops ?}. Experiments are conducted with and without the log compression (see Section \ref{sec:logcomp}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with log compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without log compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

Irrespective of the rank $k$ considered, best result is achieved for the time-scattering with log compression using the \emph{ob-c} approach. Overall, the time scattering with the log compression outperform the MFCCs systematically.

@@

Outcomes for the time-scattering with and without log compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the log compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the log compression. \gl{une idée du pourquoi ?}

>>>>

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients \gl{vincent: windows and hops ?}. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

Irrespective of the rank $k$ considered, best result is achieved for the time-scattering with logarithmic compression using the \emph{ob-c} approach. Overall, the time scattering with the logarithmic compression outperform the MFCCs systematically.

@@

Outcomes for the time-scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the logarithmic compression. \gl{une idée du pourquoi ?}
